% !TEX root = arbeit.tex
% Damit Latex weiss, wo die main Datei ist.
\section{Introduction}

	\subsection{Mission}
	Motivation to fly to Jupiter and his Icy moons. Mission explanation with an explanation why TOFs are used and better than other types of sensors to analyse the moons exospheres (Refs. to Audrey, Salome...).\\
	If there is an explanation where TOFs were used so far, than its in this chapter. In the next there is only technical staff about TOFs. For references see Paper and Rico's diss.\\
	JUICE PEP NIM
	
	\subsection{Requirements}
	Mass, performance, Power consumption. (See latest references. Part of the introduction?)
	Either give a short overview with references to the different subchapters in the Disseration as a guideline. At that point, the people don't know anything about the instrument.
	
	\subsection{Diss Overview} % is currently the start of the theory part.
	Scope of the thesis. Give a short overview over the chapter to explain that in the theory part the different compartments are analysed from the theoretical point of view and in the experimental part, there are made tests of the different compartments. Does it make sense to do it so if there is not explained how the spectrometer works? Only stat it on a very rudimentary level.	
	
	% Rico's Diss
	\begin{comment}
	Planetology depends on simulations but there are also instruments needed to verify the models and set constrains for them. Optical techniques as ultraviolet (UV), visible (VIS), infrared (IR) spectroscopy. On space craft or on earth such as ALMA...
	laser ionization mass spectroscopy (LIMS) for lander to analyse the soil.
	Mass spectrometry has better sensitivity because there single atoms are counted 
	
	\end{comment}
		
	\begin{comment}
		Why a TOF compared to other types of mass spectrometers such as sector magnets or quadrupols.Costumisatoin to the needs of the of the mission (GC for NGMS).
		Improvement in the electronics.
	\end{comment}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	